Choose a License

### 2024-12-15 choose_license.qmd
Mention full text and code disclosure requirements

- __Attribution__ means whether recipients of your work are required to provide attribution to you. For software licenses, the attribution is part of a copyright notice. Note that even if attribution is not a requirement of the license, good scientific practice demands that appropriate citations are made.
- __State changes__ means that recipients need to indicate if changes were made.
- __Anti-DRM__ means that when others share your work they are not allowed to apply technological measures restricting anything that the license permits. Implementing such restrictive measures is also referred to as **d**igital **r**ights **m**anagement (DRM).

@@

  type --"Software"--> code_sa("Attribution?<br>State changes?<br>Copyleft?")
  type --"Writing, image, audio, video"--> nocode_cc("Attribution?<br>State changes?<br>Anti-DRM?<br>Copyleft?")

  code_sa --"Attribution &<br>State changes"--> apache["Apache 2.0"]
  code_sa --"Attribution &<br>Weak copyleft"--> mpl["MPL 2.0"]
  code_sa --"Attribution &<br>State changes &<br>Strong copyleft"--> agpl["AGPLv3"]

>>>>

- __Attribution__ means whether recipients of your work are required to provide attribution to you. For software licenses, the attribution is part of a copyright notice. Note that even if attribution is not a requirement of the license, good scientific practice demands that appropriate citations are made.
- __Add license text__ means that recipients need to distribute the full text of the license along with the work (rather than only mentioning its license, for example, via a link).
- __State changes__ means that recipients need to indicate if changes were made.
- __Disclose code__ means that recipients need to disclose the source code when distributing modified versions of your work.
- __Anti-DRM__ means that when others share your work they are not allowed to apply technological measures restricting anything that the license permits. Implementing such restrictive measures is also referred to as **d**igital **r**ights **m**anagement (DRM).

@@

  type --"Software"--> code_sa("Attribution?<br>Add license text?<br>State changes?<br>Disclose code?<br>Copyleft?")
  type --"Writing, image, audio, video"--> nocode_cc("Attribution?<br>State changes?<br>Anti-DRM?<br>Copyleft?")

  code_sa --"Attribution &<br>Add license text &<br>State changes"--> apache["Apache 2.0"]
  code_sa --"Attribution &<br>Disclose code &<br>Weak copyleft"--> mpl["MPL 2.0"]
  code_sa --"Attribution &<br>Add license text &<br>State changes &<br>Disclose code &<br>Strong copyleft"--> agpl["AGPLv3"]
